Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-24 paper.tex
improving introduction: Closes #6

Thus, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will
achieve, in order to optimise production schedules, improve the publishing
company profits or minimise losses \cite{Zhao2001}. This is the main
objective of this paper. 
%FERGU: entonces el objetivo es desarrollar una herramienta? La
%metodología? Dejarlo más claro en todos los sitios
% Un método predictivo. Lo deja muy claro - JJ
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir
% un poco más lo que se hace en ese trabajo. ;)
% An example of what? Does that go there or to the state of the art? - JJ

The accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}. % This
                                % paragraph is rather useless - JJ
% I have changed the paragraph completely, but still don't know what
% this is doing here - JJ

>>>>

Thus, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will
achieve, in order to optimise production schedules, improve the publishing
company profits or minimise losses \cite{Zhao2001}, 
being this the main objective of this paper: optimizing sales and
improving profit margins by selling the whole print-run.

In any case, the accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}. % This
                                % paragraph is rather useless - JJ
% I have changed the paragraph completely, but still don't know what
% this is doing here - JJ
